PANCHANGE_analysis

### 2020-12-16 PANCHANGE_analysis.Rmd
knitted exclusion file with all datasets updated for employment

```{r model1b employment prior covid function}
model1b.estimates <- function(outcome, data_set) {
  # define the variable name of the dependent variable
  dependent.variable <- outcome
  # define the independent variables
  independent.variables <- c("depression_and_anxiety",
                             "eating_disorders",
                             "obsessive_compulsive_disorders",
                             "bipolar_and_schizophrenia",
                             "mhd.posttraumatic_stress_disorder_ptsd",
                             "autism_spectrum_disorder",
                             "mhd.attention_deficit_hyperactivity_disorder",
                             "mhd.personality_disorder",
                             "Gender_collapsed",
                             "age_category_collapsed",
                             "Ethnicity_collapsed",
                             "key_worker",
                             "time_diff_coping_lockdown_march_23",
                             "employment_prior_covid"
                                )
  # create the formula
  glm.formula <- as.formula(paste(dependent.variable, paste(independent.variables, collapse=" + "), sep=" ~ "))
  glm.formula

@@

@@

```{r model1b.explan employment prior covid function}
model1b.explan.estimates <- function(outcome, explan_var, data_set) {
  # define the variable name of the dependent variable
  dependent.variable <- outcome
  # define the independent variables
  independent.variables <- c(explan_var,
                             "depression_and_anxiety",
                             "eating_disorders",
                             "obsessive_compulsive_disorders",
                             "bipolar_and_schizophrenia",
                             "mhd.posttraumatic_stress_disorder_ptsd",
                             "autism_spectrum_disorder",
                             "mhd.attention_deficit_hyperactivity_disorder",
                             "mhd.personality_disorder",
                             "Gender_collapsed",
                             "age_category_collapsed",
                             "Ethnicity_collapsed",
                             "key_worker",
                             "time_diff_coping_lockdown_march_23",
                             "employment_prior_covid"
  )
  # create the formula
  glm.formula <- as.formula(paste(dependent.variable, paste(independent.variables, collapse=" + "), sep=" ~ "))
  glm.formula

@@

  ## Row labels
  independent.variables <- c("intercept",
                             explan_var,
                             "comorbid depression and anxiety compared to control",
                             "depressive disorder compared to control",
                             "anxiety disorder compared to control",
                             "eating disorders compared to control",
                             "obsessive compulsive disorders compared to control",
                             "comorbid psychotic and bipolar disorder compared to control",
                             "psychotic disorder compared to control",
                             "bipolar disorder compared to control",
                             "mhd.posttraumatic_stress_disorder_ptsd compared to control",
                             "autism_spectrum_disorder compared to control",
                             "mhd.attention_deficit_hyperactivity_disorder compared to control",
                             "mhd.personality_disorder compared to control",
                             "Female compared to male",
                             "Non-binary/Self-defined compared to male",
                             "16-18 compared to 26-35",
                             "19-25 compared to 26-35",
                             "36-45 compared to 26-35",
                             "46-55 compared to 26-35",
                             "56-65 compared to 26-35",
                             "66-70 compared to 26-35",
                             "71-75 compared to 26-35",
                             "76+ compared to 26-35",
                             "Mixed or multiple ethnicities compared to White",
                             "Asian compared to White",
                             "Black compared to White",
                             "Other compared to White",
                             "key_worker compared to non-keyworker",
                             "time_diff_coping_lockdown_march_23")
  ## categories to facet on  
  categories <- c("Intercept",
                  "Pre-existing mental health",
                  "Pre-existing mental health",
                  "Pre-existing mental health",
                  "Pre-existing mental health",
                  "Pre-existing mental health",
                  "Pre-existing mental health",
                  "Pre-existing mental health",
                  "Pre-existing mental health",
                  "Pre-existing mental health",
                  "Pre-existing mental health",
                  "Pre-existing mental health",
                  "Pre-existing mental health",
                  "Pre-existing mental health",
                  "Gender",
                  "Gender",
                  "Age",
                  "Age",
                  "Age",
                  "Age",
                  "Age",
                  "Age",
                  "Age",
                  "Age",
                  "Ethnicity",
                  "Ethnicity",
                  "Ethnicity",
                  "Ethnicity",
                  "Other",
                  "Other")

  ## Disoprder dimension  
  groups <- c(group,
              group,
              group,
              group,
              group,
              group,
              group,
              group,
              group,
              group,
              group,
              group,
              group,
              group,
              group,
              group,
              group,
              group,
              group,
              group,
              group,
              group,
              group,
              group,
              group,
              group,
              group,
              group,
              group,
              group)

@@

  # define the variable name of the dependent variable
  dependent.variable <- outcome
  # define the independent variables
  independent.variables <- c(explan_var,
                             "depression_and_anxiety",
                             "eating_disorders",
                             "obsessive_compulsive_disorders",
                             "bipolar_and_schizophrenia",
                             "mhd.posttraumatic_stress_disorder_ptsd",
                             "autism_spectrum_disorder",
                             "mhd.attention_deficit_hyperactivity_disorder",
                             "mhd.personality_disorder",
                             "Gender_collapsed",
                             "age_category_collapsed_reordered",
                             "Ethnicity_collapsed",
                             "key_worker",
                             "time_diff_coping_lockdown_march_23"
  )
  # create the formula
  glm.formula <- paste(dependent.variable, paste(independent.variables, collapse=" + "), sep=" ~ ")

>>>>

```{r model1b employment prior covid function}
model1b.estimates <- function(outcome, data_set) {
  # define the variable name of the dependent variable
  dependent.variable <- outcome
  # define the independent variables
  independent.variables <- c("depression_and_anxiety",
                             "eating_disorders",
                             "obsessive_compulsive_disorders",
                             "bipolar_and_schizophrenia",
                             "mhd.posttraumatic_stress_disorder_ptsd",
                             "autism_spectrum_disorder",
                             "mhd.attention_deficit_hyperactivity_disorder",
                             "mhd.personality_disorder",
                             "Gender_collapsed",
                             "age_category_collapsed",
                             "Ethnicity_collapsed",
                             "time_diff_coping_lockdown_march_23",
                             "employment_prior_covid"
                                )
  # create the formula
  glm.formula <- as.formula(paste(dependent.variable, paste(independent.variables, collapse=" + "), sep=" ~ "))
  glm.formula

@@

               "employment_prior_covidKey worker" = "Key worker",

@@

```{r model1b.explan employment prior covid function}
model1b.explan.estimates <- function(outcome, explan_var, data_set) {
  # define the variable name of the dependent variable
  dependent.variable <- outcome
  # define the independent variables
  independent.variables <- c(explan_var,
                             "depression_and_anxiety",
                             "eating_disorders",
                             "obsessive_compulsive_disorders",
                             "bipolar_and_schizophrenia",
                             "mhd.posttraumatic_stress_disorder_ptsd",
                             "autism_spectrum_disorder",
                             "mhd.attention_deficit_hyperactivity_disorder",
                             "mhd.personality_disorder",
                             "Gender_collapsed",
                             "age_category_collapsed",
                             "Ethnicity_collapsed",
                             "time_diff_coping_lockdown_march_23",
                             "employment_prior_covid"
  )
  # create the formula
  glm.formula <- as.formula(paste(dependent.variable, paste(independent.variables, collapse=" + "), sep=" ~ "))
  glm.formula

@@

  ## Row labels
  independent.variables <- c("intercept",
                             explan_var,
                             "comorbid depression and anxiety compared to control",
                             "depressive disorder compared to control",
                             "anxiety disorder compared to control",
                             "eating disorders compared to control",
                             "obsessive compulsive disorders compared to control",
                             "comorbid psychotic and bipolar disorder compared to control",
                             "psychotic disorder compared to control",
                             "bipolar disorder compared to control",
                             "mhd.posttraumatic_stress_disorder_ptsd compared to control",
                             "autism_spectrum_disorder compared to control",
                             "mhd.attention_deficit_hyperactivity_disorder compared to control",
                             "mhd.personality_disorder compared to control",
                             "Female compared to male",
                             "Non-binary/Self-defined compared to male",
                             "16-18 compared to 26-35",
                             "19-25 compared to 26-35",
                             "36-45 compared to 26-35",
                             "46-55 compared to 26-35",
                             "56-65 compared to 26-35",
                             "66-70 compared to 26-35",
                             "71-75 compared to 26-35",
                             "76+ compared to 26-35",
                             "Mixed or multiple ethnicities compared to White",
                             "Asian compared to White",
                             "Black compared to White",
                             "Other compared to White",
                             "key_worker compared to employed",
                             "unemployed compared to employed",
                             "student compared to employed",
                             "retired compared to employed",
                             "time_diff_coping_lockdown_march_23")
  ## categories to facet on  
  categories <- c("Intercept",
                  "Pre-existing mental health",
                  "Pre-existing mental health",
                  "Pre-existing mental health",
                  "Pre-existing mental health",
                  "Pre-existing mental health",
                  "Pre-existing mental health",
                  "Pre-existing mental health",
                  "Pre-existing mental health",
                  "Pre-existing mental health",
                  "Pre-existing mental health",
                  "Pre-existing mental health",
                  "Pre-existing mental health",
                  "Pre-existing mental health",
                  "Gender",
                  "Gender",
                  "Age",
                  "Age",
                  "Age",
                  "Age",
                  "Age",
                  "Age",
                  "Age",
                  "Age",
                  "Ethnicity",
                  "Ethnicity",
                  "Ethnicity",
                  "Ethnicity",
                  "Employment",
                  "Employment",
                  "Employment",
                  "Employment",
                  "Other")

  ## Disorder dimension  
  groups <- c(group,
              group,
              group,
              group,
              group,
              group,
              group,
              group,
              group,
              group,
              group,
              group,
              group,
              group,
              group,
              group,
              group,
              group,
              group,
              group,
              group,
              group,
              group,
              group,
              group,
              group,
              group,
              group,
              group,
              group,
              group,
              group,
              group)

@@

  # define the variable name of the dependent variable
  dependent.variable <- outcome
  # define the independent variables
  independent.variables <- c(explan_var,
                             "depression_and_anxiety",
                             "eating_disorders",
                             "obsessive_compulsive_disorders",
                             "bipolar_and_schizophrenia",
                             "mhd.posttraumatic_stress_disorder_ptsd",
                             "autism_spectrum_disorder",
                             "mhd.attention_deficit_hyperactivity_disorder",
                             "mhd.personality_disorder",
                             "Gender_collapsed",
                             "age_category_collapsed_reordered",
                             "Ethnicity_collapsed",
                             "employment_prior_covid",
                             "time_diff_coping_lockdown_march_23"
  )
  # create the formula
  glm.formula <- paste(dependent.variable, paste(independent.variables, collapse=" + "), sep=" ~ ")
